%-----------------------------------------------------------------------------
% Author: Rayla Kurosaki
% GitHub: https://github.com/rkp1503
%-----------------------------------------------------------------------------
\documentclass{rayla-project}
\usepackage{rayla-style}

%-----------------------------------------------------------------------------
% Project Information
%-----------------------------------------------------------------------------
\myUniversity{
    Rochester Institute of Technology\\
    College of Science\\
    School of Mathematical Sciences
    }
\myTitle{Red Blood Cell Production}
\myName{Ramsey (Rayla) Phuc}
\courseid{MATH-421.01}
\courseName{Mathematical Modeling}
\professorName{Dr. Nathan Cahill}
\term{2020-2021 Fall}
\dueDate{December 7th, 2020}

%-----------------------------------------------------------------------------
% Start of Document
%-----------------------------------------------------------------------------
\begin{document}

    \maketitle

    %-------------------------------------------------------------------------
    % Abstract
    %-------------------------------------------------------------------------
    \begin{abstract}
        Red Blood Cells are present in the human body and their purpose is to deliver oxygen to the human body while giving carbon dioxide for humans to exhale. The purpose of this paper is to show that Red Blood Cells can maintain an equilibrium state if a certain condition is met. Multiple models have been tested to show that this condition is consistent given the proper assumptions. The first model being analyzed is a system of linear difference equations. The second model being analyzed is a system of linear differential equations. The third model being analyzed is also a system of linear difference equations with the assumption that the spleen removes a portion of Red Blood Cells based on the number of Red Blood Cells present in the human body. In particular, as the number of Red Blood Cells in the human body increases, the portion of Red Blood Cells filtered out by the spleen will increase non-linearly. This condition is where $\gamma = 1$.
    \end{abstract}

    %-------------------------------------------------------------------------
    % Body
    %-------------------------------------------------------------------------
    \input{contents/chapter01.tex}
    \input{contents/chapter02.tex}
    \input{contents/chapter03.tex}
    \input{contents/chapter04.tex}
    \input{contents/chapter05.tex}
    \input{contents/chapter06.tex}

    %-------------------------------------------------------------------------
    % Bibliography
    %-------------------------------------------------------------------------
    \newpage
    % \nocite{*}
    \printbibliography[title={Bibliography}]

\end{document}
